Do we need detailed demographic data to forecast plant population responses to climate change?

### 2015-02-25 manuscript/manuscript.Rmd
updated figures for climate change sim

```{r figure_2, dependson="plot-options", fig.cap="Simulated changes species' median cover caused by a 1% increase in observed precipitation or temperature. We used the median of simulated results because the average was highly influence by some extreme outliers.", fig.width=6.5, fig.height=4, cache=FALSE, results='hide'}
climBase <- readRDS("../montana/quadBM/simulations/baselineSimulationQBM.rds")
climPpt <- readRDS("../montana/quadBM/simulations/pptChangeSimulationQBM.rds")
climTemp <- readRDS("../montana/quadBM/simulations/tempChangeSimulationQBM.rds")
climBoth <- readRDS("../montana/quadBM/simulations/temp-pptChangeSimulationQBM.rds")
climBase$sim <- rep("AObserved", nrow(climBase)) 
climPpt$sim <- rep("BPrecipitation", nrow(climBase)) 
climTemp$sim <- rep("CTemperature", nrow(climBase)) 
climBoth$sim <- rep("DBoth", nrow(climBase)) 
climSimsQBM <- rbind(climBase, climPpt, climTemp, climBoth)

myCols2 <- c("grey45", "#277BA8", "#7ABBBD", "#AED77A")
ggplot(climSimsQBM)+
  geom_boxplot(aes(x=species, y=cover*100, fill=sim), outlier.size=0)+
  theme_bw()+
  coord_cartesian(ylim=c(0,50))+
  scale_fill_manual(name="", labels=c("Observed", "1% Precipitation Increase", "1% Temperature Increase", "1% Temp. & Ppt. Increase"), values=myCols2)

>>>>

```{r figure_2, dependson="plot-options", fig.cap="Changes in species' mean cover caused by a 1% increase in observed precipitation or temperature as predicted by the individual-based IPM and the aggregate-based QBM. Note that the change for POSE due to a precipitation increase predicted by the QBM is almost zero and so does not show up in the figure.", fig.width=6.5, fig.height=6, cache=FALSE, results='hide'}
climBase <- readRDS("../montana/quadBM/simulations/baselineSimulationQBM.rds")
climPpt <- readRDS("../montana/quadBM/simulations/pptChangeSimulationQBM.rds")
climTemp <- readRDS("../montana/quadBM/simulations/tempChangeSimulationQBM.rds")
climBoth <- readRDS("../montana/quadBM/simulations/temp-pptChangeSimulationQBM.rds")
climBase$sim <- rep("AObserved", nrow(climBase)) 
climPpt$sim <- rep("BPrecipitation", nrow(climBase)) 
climTemp$sim <- rep("CTemperature", nrow(climBase)) 
climBoth$sim <- rep("DBoth", nrow(climBase)) 
climSimsQBM <- rbind(climBase, climPpt, climTemp, climBoth)
qbm_means <- ddply(climSimsQBM, .(species, sim), summarise,
                   avg_cover = mean(cover))
tmpid <- which(qbm_means$sim=="AObserved")
diffs <- list()
for(i in 1:length(tmpid)){
  obs <- qbm_means[tmpid[i],"avg_cover"]
  diffs[[i]] <- rep(obs,3) - qbm_means[(tmpid[i]+1):(tmpid[i]+3), "avg_cover"]
}
names(diffs) <- unique(qbm_means$species)
diff_df <- melt(as.data.frame(diffs))
diff_df$sim <- rep(c("pptChange", "tempChange", "temppptChange"),4)
diff_df$type <- rep("QBM", nrow(diff_df))

ipm_diffs <- readRDS("../montana/ipm/simulations/results/ipm_climatesims_percdiffs.rds")
ipm_diffs$type <- rep("IPM", nrow(ipm_diffs))

diff_df <- rbind(diff_df, ipm_diffs)

myCols2 <- c("grey45", "#277BA8", "#7ABBBD", "#AED77A")
# ggplot(climSimsQBM)+
#   geom_boxplot(aes(x=species, y=cover*100, fill=sim), outlier.size=0)+
#   theme_bw()+
#   coord_cartesian(ylim=c(0,50))+
#   scale_fill_manual(name="", labels=c("Observed", "1% Precipitation Increase", "1% Temperature Increase", "1% Temp. & Ppt. Increase"), values=myCols2)
ggplot(diff_df, aes(x=sim, y=value, fill=type))+
  geom_bar(stat="identity", position="dodge")+
  geom_hline(aes(yintercept=0))+
  scale_fill_manual(values = myCols2[c(2,3)], name="Model type")+
  xlab("Climatic change")+
  ylab("Cover change (%)")+
  facet_wrap("variable", scales = "free")+
  scale_x_discrete(labels=c("ppt", "temp", "ppt + tmp"))+
  theme_bw()
#   theme(axis.text.x = element_text(angle = 45, hjust = 1))

### 2015-02-25 manuscript/manuscript.tex
updated figures for climate change sim

\begin{figure}[htbp]
\centering
\includegraphics{components/figure/manuscript-figure_2.pdf}
\caption{Simulated changes species' median cover caused by a 1\%
increase in observed precipitation or temperature. We used the median of
simulated results because the average was highly influence by some
extreme outliers.}
\end{figure}

>>>>

\begin{figure}[htbp]
\centering
\includegraphics{components/figure/manuscript-figure_2.pdf}
\caption{Changes in species' mean cover caused by a 1\% increase in
observed precipitation or temperature as predicted by the
individual-based IPM and the aggregate-based QBM. Note that the change
for POSE due to a precipitation increase predicted by the QBM is almost
zero and so does not show up in the figure.}
\end{figure}
